\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot,
    top=2 cm,
    bottom=2 cm,
    left=2 cm,
    right=2 cm,
    footskip=1.0 cm,
]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor} 
\definecolor{primaryColor}{RGB}{0, 0, 0}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Nuthan Reddy's Resume},
    pdfauthor={Nuthan Reddy},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[pscoord]{eso-pic}
\usepackage{calc}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{changepage}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}
\usepackage{iftex}

\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

% Use a font with proper bold support
\usepackage[T1]{fontenc}
\usepackage{charter}

% Ensure bold font works
\usepackage[T1]{fontenc}
\renewcommand{\bfdefault}{b}
\usepackage[defaultsans]{lato}
\renewcommand{\familydefault}{\sfdefault}

% Settings:
\raggedright
\AtBeginEnvironment{adjustwidth}{\partopsep0pt}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\topskip}{0pt}
\setlength{\columnsep}{0.15cm}
\pagenumbering{gobble}

\titleformat{\section}{\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{-1pt}{0.3 cm}{0.2 cm}

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}

\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.10 cm,
        parsep=0.10 cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=0 cm + 10pt
    ]
}{
    \end{itemize}
}

\newenvironment{onecolentry}{
    \begin{adjustwidth}{0 cm + 0.00001 cm}{0 cm + 0.00001 cm}
}{
    \end{adjustwidth}
}

\newenvironment{twocolentry}[2][]{
    \onecolentry
    \def\secondColumn{#2}
    \setcolumnwidth{\fill, 4.5 cm}
    \begin{paracol}{2}
}{
    \switchcolumn \raggedleft \secondColumn
    \end{paracol}
    \endonecolentry
}

\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\linespread{1.5}
}{
    \par\kern\topsep
}

\begin{document}

\begin{header}
    \fontsize{13 pt}{13 pt}\selectfont \textbf{NUTHAN REDDY VADDI REDDY}
    
    \vspace{0.5pt}
    
    \normalsize
    nuthanreddy001@gmail.com\hspace{0.5pt}| \hspace{0.5pt}
    +1682-406-56-46\hspace{0.5pt}| \hspace{0.5pt}
    github.com/Nuthanreddy05\hspace{0.5pt}| \hspace{0.5pt}
    www.linkedin.com/in/nuthan-reddy-vaddi-reddy
\end{header}

\section{Summary}
\begin{onecolentry}
    Software Engineer with 4+ years of experience building scalable web applications and distributed systems. Specialized in React, Node.js, Python, and AWS. Proven track record of improving system reliability by 24\% and optimizing API latency by 31\% in high-traffic enterprise environments.
\end{onecolentry}

\vspace{0.2cm}

\section{Experience}

\begin{twocolentry}{May 2024 -- Present}
    \textbf{Software Engineer}, Albertsons -- Dallas, TX
\end{twocolentry}
\begin{onecolentry}
\begin{highlights}
\item Designed and developed cloud-based microservices using Python and Node.js, improving service reliability by \textbf{24\%} in customer-facing applications.
\item Built and deployed RESTful APIs supporting large-scale distributed systems, reducing request latency by \textbf{31\%} through optimized service design.
\item Implemented CI/CD pipelines on AWS using GitHub Actions and cloud-native tooling, shortening release cycles by \textbf{28\%}.
\item Translated business and technical requirements into scalable application features, delivering enhancements within \textbf{2--4} month project timelines.
\item Developed secure backend services with role-based access controls, reducing security-related defects by \textbf{19\%}.
\item Supported multi-page web applications using React and JavaScript, improving frontend load performance by \textbf{22\%}.
\item Analyzed and processed large transactional datasets to support application logic, improving data-processing throughput by \textbf{35\%}.
\item Authored technical documentation covering system architecture, API contracts, and deployment workflows, accelerating team onboarding by \textbf{21\%}.
\item Collaborated with product managers and architects to evaluate new technologies, contributing to \textbf{3} successful proof-of-concept implementations.
\item Troubleshot and debugged production issues across distributed services, reducing mean-time-to-resolution by \textbf{18\%}.
\item Coordinated development priorities with a \textbf{4}-member agile team, consistently meeting sprint delivery commitments.
\item Provided guidance and code reviews for junior engineers, improving code quality and reducing rework by \textbf{16\%}.
\end{highlights}
\end{onecolentry}

\vspace{0.2cm}

\begin{twocolentry}{May 2020 -- July 2023}
    \textbf{Software Engineer}, ValueLabs -- Hyderabad
\end{twocolentry}
\begin{onecolentry}
\begin{highlights}
\item Developed multi-page web applications using React, JavaScript, and Python, supporting business workflows for enterprise clients.
\item Implemented backend services using Java and Python, improving application stability by \textbf{20\%} across supported modules.
\item Designed and maintained microservice-based architectures, enabling independent scaling of services and reducing deployment risk.
\item Built and optimized SQL-based data access layers, improving query performance by \textbf{26\%}.
\item Supported cloud-based delivery environments on AWS, assisting with deployments and configuration management.
\item Processed and analyzed large, complex datasets to support application features, improving response accuracy by \textbf{14\%}.
\item Ensured software security by implementing input validation, authentication checks, and secure coding practices.
\item Participated in full software development lifecycle activities including design, development, testing, and release management.
\item Collaborated with cross-functional teams to gather requirements and translate them into technical solutions.
\item Debugged and resolved application defects, reducing recurring production issues by \textbf{17\%}.
\item Contributed to UI design and development efforts, improving usability scores by \textbf{15\%}.
\item Mentored junior developers on coding standards and debugging techniques, improving team productivity by \textbf{13\%}.
\end{highlights}
\end{onecolentry}

\vspace{0.2cm}

\section{Academic Project Experience}

\begin{twocolentry}{Jan 2024 -- May 2024}
    \textbf{Cloud-Native Distributed Application Development}
\end{twocolentry}
\begin{onecolentry}
\begin{highlights}
\item Designed a cloud-based distributed system using AWS services, supporting scalable application workloads.
\item Developed backend services in Python and Node.js with REST APIs to handle concurrent requests efficiently.
\item Implemented CI/CD pipelines for automated testing and deployment, reducing manual release effort by \textbf{30\%}.
\item Built a React-based frontend to support multi-page user interactions with backend services.
\item Applied security best practices including authentication and access control across services.
\item Documented system design, trade-offs, and deployment architecture in a comprehensive technical report.
\end{highlights}
\end{onecolentry}

\vspace{0.2cm}

\begin{twocolentry}{Aug 2023 -- Dec 2023}
    \textbf{Web Application Architecture and Optimization Project}
\end{twocolentry}
\begin{onecolentry}
\begin{highlights}
\item Designed and developed a full-stack web application using React, Python, and SQL.
\item Optimized backend data access patterns, improving response times by \textbf{23\%}.
\item Implemented modular UI components to improve maintainability and reuse.
\item Conducted functional and integration testing to validate application behavior.
\item Analyzed performance bottlenecks and applied targeted improvements.
\item Delivered the project within a \textbf{4}-month academic timeline with complete documentation.
\end{highlights}
\end{onecolentry}

\vspace{0.2cm}

\section{Technical Skills}
\begin{minipage}[t]{\linewidth}
\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=2pt]
\item Programming: Python, Java, JavaScript, Node.js
\item Web Technologies: React, REST APIs, HTML, CSS
\item Cloud Platforms: AWS (CI/CD, deployment, environment management)
\item Software Engineering: Microservices, distributed systems, SDLC, secure coding
\item Databases: SQL, relational database design, data access optimization
\item Tools \& Practices: Git, CI/CD pipelines, debugging, technical documentation
\end{itemize}
\end{minipage}

\vspace{0.2cm}

\section{Education}
\begin{twocolentry}{Aug 2023 -- May 2025}
    \textbf{The University of Texas at Arlington,} MS in Data Science
\end{twocolentry}
\begin{onecolentry}
\begin{highlights}
    \item \textbf{GPA:} 3.8/4.0
    \item \textbf{Relevant Coursework:} Distributed Systems, Cloud Computing, Software Engineering, Data Structures, Algorithms, Machine Learning
\end{highlights}
\end{onecolentry}

\end{document}
