\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot,
    top=2 cm,
    bottom=2 cm,
    left=2 cm,
    right=2 cm,
    footskip=1.0 cm,
]{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor} 
\definecolor{primaryColor}{RGB}{0, 0, 0}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Nuthan Reddy's Resume},
    pdfauthor={Nuthan Reddy},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[pscoord]{eso-pic}
\usepackage{calc}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{changepage}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}
\usepackage{iftex}

\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

% Use a font with proper bold support
\usepackage[T1]{fontenc}
\usepackage{charter}

% Ensure bold font works
\usepackage[T1]{fontenc}
% Font configuration - Switch to Helvetica (Arial-like) for better Tectonic compatibility
\usepackage{tgheros} 
\renewcommand{\familydefault}{\sfdefault}

% Settings:
\raggedright
\AtBeginEnvironment{adjustwidth}{\partopsep0pt}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\topskip}{0pt}
\setlength{\columnsep}{0.15cm}
\pagenumbering{gobble}

\titleformat{\section}{\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{-1pt}{0.3 cm}{0.2 cm}

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}

\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.10 cm,
        parsep=0.10 cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=0 cm + 10pt
    ]
}{
    \end{itemize}
}

\newenvironment{onecolentry}{
    \begin{adjustwidth}{0 cm + 0.00001 cm}{0 cm + 0.00001 cm}
}{
    \end{adjustwidth}
}

\newenvironment{twocolentry}[2][]{
    \onecolentry
    \def\secondColumn{#2}
    \setcolumnwidth{\fill, 4.5 cm}
    \begin{paracol}{2}
}{
    \switchcolumn \raggedleft \secondColumn
    \end{paracol}
    \endonecolentry
}

\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\linespread{1.5}
}{
    \par\kern\topsep
}

\begin{document}

\begin{header}
    \fontsize{13 pt}{13 pt}\selectfont \textbf{NUTHAN REDDY VADDI REDDY}
    
    \vspace{0.5pt}
    
    \normalsize
    nuthanreddy001@gmail.com\hspace{0.5pt}| \hspace{0.5pt}
    +1682-406-56-46\hspace{0.5pt}| \hspace{0.5pt}
    github.com/Nuthanreddy05\hspace{0.5pt}| \hspace{0.5pt}
    www.linkedin.com/in/nuthan-reddy-vaddi-reddy
\end{header}

\section{Summary}
\begin{onecolentry}
    DevOps Engineer with 4 years of experience in infrastructure automation and system reliability engineering. Specialized in Linux, Ansible, Jenkins, Python, and monitoring stack implementation. Proven track record of improving system reliability by \textbf{27\%} and reducing operational costs by \textbf{\$47K} annually. Currently contributing to Albertsons' IT infrastructure team by building and maintaining scalable automation systems for 2,300+ stores and 8 million weekly customers. Focused on implementing robust CI/CD pipelines and observability solutions to support enterprise retail operations.
\end{onecolentry}

\vspace{0.2cm}

\section{Experience}

\begin{twocolentry}{May 2024 -- Present}
    \textbf{DevOps Engineer}, Albertsons -- Dallas, TX
\end{twocolentry}
\begin{onecolentry}

\begin{highlights}
    
    \item DevOps engineer on IT infrastructure team managing cloud platform operations and automation systems for 2,300+ stores, supporting reliable e-commerce and payment processing for millions of weekly customers.
    
    \item Developed Ansible automation playbooks for Linux server configuration management across Albertsons' infrastructure using Python and Bash, contributing to \textbf{27\%} improvement in deployment consistency for 500+ virtual machines.
    
    \item Contributed to monitoring platform initiative by implementing Prometheus exporters and Grafana dashboards for VictoriaMetrics, supporting \textbf{58\%} reduction in mean time to detection for production incidents.
    
    \item Built Jenkins pipeline configurations for CI/CD workflows using scripted pipelines and Git integration, achieving \textbf{41\%} faster deployment cycles for microservices supporting payment systems.
    
    \item Contributed to database reliability team by implementing ClickHouse monitoring solutions with custom Python scripts, improving query performance visibility by \textbf{34\%} for analytics workloads.
    
    \item Faced with manual server provisioning challenges, implemented automated bare metal deployment system using Ansible and custom Bash scripts, reducing setup time by \textbf{73\%} for new store infrastructure.
    
    \item Contributed to network security enhancement by implementing iptables automation and monitoring using Python and Graylog integration, supporting \textbf{67\%} reduction in unauthorized access attempts.
    
\end{highlights}

\end{onecolentry}

\vspace{0.2cm}

\begin{twocolentry}{May 2020 -- July 2023}
    \textbf{DevOps Engineer}, ValueLabs -- Hyderabad
\end{twocolentry}
\begin{onecolentry}

\begin{highlights}
    
    \item Supported enterprise clients across retail and finance industries by building infrastructure automation platforms that improved system reliability and operational efficiency for diverse business applications.
    
    \item Developed Ansible automation for Linux server management across client environments using Ubuntu and Bash scripting, improving configuration consistency by \textbf{23\%} for 200+ servers.
    
    \item Built Jenkins CI/CD pipelines for application deployment workflows, reducing manual deployment effort by \textbf{29\%} for enterprise web applications.
    
    \item Implemented monitoring solutions using Prometheus and Grafana for client infrastructure, improving system visibility by \textbf{31\%} across distributed environments.
    
    \item Developed Python automation scripts for routine operational tasks including log analysis and backup management, reducing manual intervention by \textbf{26\%}.
    
    \item Configured and maintained virtual machine infrastructure using KVM and libvirt, supporting 50+ VMs for development and testing environments.
    
\end{highlights}

\end{onecolentry}

\vspace{0.2cm}


\section{Academic Project Experience}


\begin{twocolentry}{Aug 2023 -- Dec 2023}
    \textbf{Infrastructure Automation and Monitoring Platform}
\end{twocolentry}
\begin{onecolentry}

\begin{highlights}
    
    \item Designed automated infrastructure provisioning system using Ansible and Python for simulated retail environment with 50+ virtual machines.
    
    \item Implemented comprehensive monitoring stack with Prometheus, VictoriaMetrics, and Grafana for system metrics collection and visualization.
    
    \item Developed custom Python exporters and Bash scripts for monitoring data collection, achieving \textbf{41\%} improvement in metric coverage during validation testing.
    
    \item Built Jenkins pipeline configurations for automated testing and deployment of monitoring components in academic environment.
    
\end{highlights}

\end{onecolentry}

\vspace{0.2cm}

\begin{twocolentry}{Jan 2024 -- Apr 2024}
    \textbf{CI/CD Pipeline Optimization for Distributed Systems}
\end{twocolentry}
\begin{onecolentry}

\begin{highlights}
    
    \item Architected Jenkins-based CI/CD pipeline for distributed application deployment in graduate research project.
    
    \item Implemented automated testing stages and deployment workflows using scripted pipelines and Git integration.
    
    \item Developed Python monitoring scripts and Grafana dashboards for pipeline performance tracking, achieving \textbf{34\%} reduction in build failures during load testing scenarios.
    
    \item Configured automated security scanning and compliance checks as part of deployment workflow for proof-of-concept system.
    
\end{highlights}

\end{onecolentry}

\vspace{0.2cm}


\section{Technical Skills}
\begin{minipage}[t]{\linewidth}

\begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=2pt]

\item Operating Systems \& Infrastructure: Linux (Ubuntu), Servers (VMs, bare metal), Networking (TCP/IP, iptables), Software RAID, LVM, Full Disk Encryption

\item Automation \& Configuration: Ansible, Bash, Python, Git, CI/CD, Jenkins, Scripted Pipelines

\item Monitoring \& Observability: Prometheus, VictoriaMetrics, Grafana, Graylog, Metrics Collection, Alerting

\item Databases \& Data Systems: ClickHouse, MongoDB, Kafka, JupyterHub, Airflow, SQL

\item Cloud \& Virtualization: AWS, Azure, Docker, Kubernetes, Virtualization

\item Development \& Scripting: Python, Java, JavaScript, REST APIs, Microservices, Distributed Systems

\end{itemize}

\end{minipage}

\vspace{0.2cm}

\section{Education}
\begin{twocolentry}{Aug 2023 -- May 2025}
    \textbf{The University of Texas at Arlington,} MS in Data Science
\end{twocolentry}
\begin{onecolentry}
\begin{highlights}
    \item \textbf{GPA:} 3.8/4.0
    \item \textbf{Relevant Coursework:} Distributed Systems, Cloud Computing, Software Engineering, Data Structures, Algorithms, Operating Systems, Network Security
\end{highlights}
\end{onecolentry}

\end{document}